Functional Pearl \\ Programming with Negative and Fractional Types

### 2012-02-19 dual.tex
reworded fractional discussion

In our case, the situation is simpler. We have an isomorphism 
{{ 1 <-> a * (1/a) }} which when used in the left-to-right direction allows the
creation of a value and a corresponding constraint on the context. 
Both the value and the constraint can flow in arbitrary ways during the computation 
but eventually in a closed program with no ``dangling'' constraints, the 
isomorphism should be used in the right-to-left direction to resolve the constraints. 
To understand the computational interpretation, consider the following example.

>>>>

In our case, the situation is simpler. If the goal is to produce a value of
type {{a * b}} and a subcomputation can only produce the {{a}}-part, it would
have type {{(a * b) / b}}. In most settings, this type would be equivalent to
{{a}}. However in our setting, the constraint that this value must eventually
fit in a larger value that supplies the {{b}} is explicitly recorded and must
be resolved. In more detail, we have an isomorphism {{ 1 <-> a * (1/a) }}
which when used in the left-to-right direction allows the creation of a value
and a corresponding constraint on the context.  Both the value and the
constraint can flow in arbitrary ways during the computation but eventually
in a closed program with no ``dangling'' constraints, the isomorphism should
be used in the right-to-left direction to resolve the constraints.  To
understand the computational interpretation, consider the following example.
